The problem and promise of scale in multilayer networks

### 2019-12-09 paper/introduction.Rmd
fin sna

Rooted in mathematical graph theory, animal social networks measures the relationships of individuals and organization of animal social systems [@krause2009; @Wey2008; @croft2008]. Social network analyses provide insight into mating behaviours, species interactions, and community structures.

Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009]

infer process from large scale pattern [@krause2009]

Structure of social networks affects evolutionary processes, population dynamics, [@kurvers2014]

>>>>

Rooted in mathematical graph theory, animal social networks measure the relationships of individuals and organization of social systems [@krause2009; @wey2008a; @croft2008]. Social network analyses provide insight into mating behaviours, interspecific interactions, and community structures [@pinter-wollman2014]. 
The structure of social networks influences population dynamics and evolutionary processes [@kurvers2014]. Nevertheless, social network analyses usually only consider a single measure of sociality, drastically simplifying the complexity of animal social systems [@finn2019].

<!-- Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009] -->

<!-- infer process from large scale pattern [@krause2009] -->
